Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-06-29 acros.tex
finalizing paper

@@

@@

\newacronym{ARCH}{ARCH}{autoregressive conditional heteroskedastic}

@@

\newacronym{ARMA}{ARMA}{autoregressive moving average}

@@

\newacronym{CASL}{CASL}{Consortium for Advanced Simulation of Light Water Reactors}

@@

@@

@@

@@

\newacronym{GCAM}{GCAM}{Global Change Assessment Model}

@@

@@

\newacronym{LMFBR}{LMFBR}{Liquid-Metal-cooled Fast Breeder Reactor}

@@

\newacronym{MARKAL}{MARKAL}{MARKet and ALlocation}

@@

\newacronym{NCSA}{NCSA}{National Center for Supercomputing Applications}

@@

\newacronym{NFC}{NFC}{Nuclear Fuel Cycle}

@@

@@

@@

@@

>>>>

\newacronym{ADS}{ADS}{Accelerator Driven System}

@@

\newacronym{ANS}{ANS}{American Nuclear Society}

@@

@@

@@

@@

\newacronym{EDF}{EDF}{Électricité de France}

@@

\newacronym{EPR}{EPR}{European Pressurized Reactors}

@@

\newacronym{EU}{EU}{European Union}

@@

\newacronym{FP}{FP}{Fission Products}

@@

\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}

@@

\newacronym{LMFBR}{LMFBR}{Liquid Metal Fast Breeder Reactor}

@@

\newacronym{LWR}{LWR}{Light Water Reactor}
\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}

@@

@@

@@

\newacronym{PRIS}{PRIS}{Power Reactor Information System}

@@

\newacronym{PWR}{PWR}{Pressurized Water Reactor}

@@

\newacronym{ThOX}{ThOX}{thorium oxide}

@@

\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}

### 2017-06-29 introduction.tex
deleted number plot for SFR deployment
finalizing paper

\section{Abstract}
The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
\cite{cne2_noauthor_2015} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{SNF}from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{SNF} mass
and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
the transition into \glspl{SFR}. The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{SNF} from other EU nations.

@@

Past research, which focuses mostly on France, has made the assumptions that additional \glspl{LWR},
namely \glspl{EPR} are constructed in order to supply \gls{SNF} required
for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2007, freynet_multiobjective_2016}.
There has been little attention in reprocessing legacy \gls{SNF} from other
EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
The present work finds that this collaborative strategy can reduce the
need to construct additional \glspl{LWR} in France.

@@

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
        \end{center}
        \caption{Timeseries of installed capacity of \gls{SFR}s}
        \label{fig:sfr_cap}
\end{figure}
\FloatBarrier

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
        \end{center}
        \caption{Timeseries of number of \gls{SFR}s}
        \label{fig:sfr_num}
\end{figure}
\FloatBarrier

\Cref{fig:sfr_cap} and \cref{fig:sfr_num} display
the \gls{SFR} number and capacity over time.
The sharp increase from 2035 to 2060 is due mainly to
French aggressive growth from 1975 to 2000.

@@

The second scenario estimates the \gls{SNF} inventory in \gls{EU} at 2050,
and reprocesses the \gls{SNF} to separate plutonium. The separated
plutonium is mixed with the depleted uranium inventory from 2050
to create \gls{MOX}, which is used in the \gls{SFR}s. The used
\gls{MOX} is also reprocessed to extract plutonium, which also
is mixed with depleted uranium to produce \gls{MOX}.

>>>>

\section{Abstract}
The French strategy recommended by 2012-2015 Commission Nationale d'Evaluation reports
\cite{noauthor_cne2_nodate} emphasizes preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{SNF}from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation is run from 1950 to 2160 for EU to track the \gls{SNF} mass
and to determine the necessary reprocessing and \gls{MOX} fabrication capacity to support
the transition into \glspl{SFR}. The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{SNF} from other EU nations.

@@

Past research, which focuses mostly on France, has made the assumptions that additional \glspl{LWR},
namely \glspl{EPR} are constructed in order to supply \gls{SNF} required
for \gls{MOX} production \cite{carre_overview_2009, martin_symbiotic_2017, freynet_multiobjective_2016}.
There also are studies on regional (European) transmutation and partitioning with fast reactors
and \gls{ADS} to reduce disposal burden \cite{fazio_study_2013, martinez-val_pateros_2009}.
There has been little attention in utilizing legacy \gls{SNF} from other
EU nations to produce \gls{MOX} for the newly deployed \glspl{SFR}.
The present work finds that this collaborative strategy can reduce the
need to construct additional \glspl{LWR} in France.

@@

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
        \end{center}
        \caption{Timeseries of installed capacity of \gls{SFR}s}
        \label{fig:sfr_cap}
\end{figure}

\Cref{fig:sfr_cap} display
the \gls{SFR} number and capacity over time.
The sharp increase from 2035 to 2060 is due mainly to
French aggressive growth from 1975 to 2000.

@@

The second scenario utilizes the obtained \gls{SNF} inventory in \gls{EU} at 2050,
and reprocesses the \gls{SNF} to separate plutonium. The separated
plutonium is mixed with the depleted uranium inventory from 2050
to create \gls{MOX}, which is used in the \gls{SFR}s. The used
\gls{MOX} is also reprocessed to extract plutonium, which also
is mixed with depleted uranium to produce \gls{MOX}. Note that the plutonium
from both spent fuel types are of 'good quality' (~70\% fissile, ~25\% Pu240),
and the \gls{MOX} fuel is fabricated in the simulation to have an appropriate
neutronic property \cite{huff_fundamental_2016}.

### 2017-06-29 results.tex
finalizing paper

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category [unit] & Value & Specifics \\ \hline
			Total UOX Usage [t] & 188,196  &  \\ \hline
			Total MOX Usage [t] & 118 & \\ \hline
			Total Spent UOX [t] & 183,807 & \\ \hline
			Total Spent MOX [t] & 0 & All is Reprocessed. \\ \hline
			Total Tailings [t] & 1,125,798 & \\ \hline
		\end{tabular}}
		\caption{Simulation Results}
		\label{tab:sim_result}
		\end {table}

@@

Tables \ref{tab:eu_num} and \ref{tab:eu_pow} display the
timeseries of number of reactors and installed capacity in \gls{EU}.

@@

Figures \ref{fig:eu_tail} and \ref{fig:snf} show the 
timeseries of mass of tailings and spent fuel accumulation in \gls{EU}.

Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.

Note that the MOX usage is so little that it is invisible in the
plot.

@@

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/eu_future/total_fuel.png}
	\end{center}
	\caption{Timeseries of total fuel usage in \gls{EU}.}
	\label{fig:eu_fuel}
\end{figure}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Isotope & Mass Fraction in Spent Fuel [\%] & Quantity [t] \\ \hline
		Total & .9358 & 1,720 \\ \hline
		Pu238 & .0111 & 20.40 \\ \hline
		Pu239 & .518 & 952.12 \\ \hline
		Pu240 & .232 & 426.43 \\ \hline
		Pu241 & .126 & 231.59 \\ \hline
		Pu242 & .0487 & 89.51 \\ \hline
	\end{tabular}
	\caption{Plutonium From Spent Fuel}
	\label{tab:pu}
\end{table}

To create \gls{MOX}, 10\% Pu and 90\% depleted uranium is used.
Thus $1,720$ tons of plutonium yields $17,200$ tons of
\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
and quantity of plutonium that can be obtained from the 2050 \gls{SNF} inventory.

@@

From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
ASTRID-type \gls{SFR} of capacity $600 MWe$ needs $1.225$ tons of
plutonium a year, with an initial plutonium loading of $4.9$ tons.
Thus, it can be assumed that the ASTRID reactor takes in $49$ tons of 
\gls{MOX}, and refuels a quarter of its fuel every year. Simply,
an ASTRID reactor needs $12.25$ tons of \gls{MOX} per year.

The number of SFR-years worth of fuel that can be created with
the \gls{SNF} from 2050 is $\frac{17,611.3 t}{12.25} = 1,437.65 $,
assuming infinite reprocessing and \gls{MOX} fabrication capacity.

However, assuming that \gls{MOX} can be recycled indefinitely,
spent \gls{MOX} from an ASTRID reactor
contains enough plutonium to produce a \gls{MOX} fuel with
the same mass, if mixed with depleted uranium. For example,
spent \gls{MOX} from an ASTRID reactor is 38\% plutonium,
whereas a fresh \gls{MOX} is 10\% plutonium.
The compositions are in \cref{tab:comp}.
Separating plutonium from spent \gls{MOX} from
an ASTRID reactor can create \gls{MOX} more than
three times the mass of spent \gls{MOX}.

@@

\Cref{fig:mox_fab} shows the progression of mox created from
the fabrication plant over time. \Cref{fig:mox_fab} shows
the separated plutonium demand from spent \gls{MOX} to fuel the 
ASTRID reactors.

\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
(any content from spent fuel other than U, Pu) over time. Note that 
the amount of reprocessing waste is much greater when reprocessing
spent \gls{MOX} from ASTRID reactors, since there is little uranium
or plutonium left due to a high burnup.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/mox_from_mixer.png}
	\end{center}
	\caption{Timeseries of MOX produced from Fabrications}
	\label{fig:mox_fab}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/pu_demand.png}
	\end{center}
	\caption{Separated Plutonium demand from Spent MOX}
	\label{fig:pu_demand_mox}
\end{figure}

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
	\end{center}
	\caption{Reprocessing Waste for French Transition Scenario.}
	\label{fig:reprocess_waste}
\end{figure}

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category [unit] & Value & Specifics \\ \hline
			Total MOX used [t] & 164,141 & \\ \hline
			Total MOX from UOX Waste [t] & 2,347.2  &  \\ \hline
			Total MOX from MOX Waste [t] & 161,793.8 & \\ \hline
		\end{tabular}}
		\caption {\gls{SFR} Simulation Results}
		\label{tab:sfr_sim_result}
\end {table}

>>>>

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category  & Value [t] & Specifics \\ \hline
			Total Natural U & 1,314,003 & \\ \hline
			Total UOX Usage  & 188,196  &  \\ \hline
			Total MOX Usage  & 118 & \\ \hline
			Total Spent UOX  & 183,992 & \\ \hline
			Total Spent MOX  & 0 & All is Reprocessed. \\ \hline
			Total Tailings  & 1,125,798 & \\ \hline
		\end{tabular}}
		\caption{Simulation Results}
		\label{tab:sim_result}
		\end {table}

@@

@@

Figures \ref{fig:eu_num} and \ref{fig:eu_pow} display the
timeseries of number of reactors and installed capacity in \gls{EU}.

Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
timeseries of mass of tailings and spent fuel accumulation in \gls{EU}.

@@

@@

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Isotope & Mass Fraction in Spent Fuel [\%] & Quantity [t] \\ \hline
		Total & .9358 & 1,721.79 \\ \hline
		Pu238 & .0111 & 20.42 \\ \hline
		Pu239 & .518 & 953.07 \\ \hline
		Pu240 & .232 & 426.86 \\ \hline
		Pu241 & .126 & 231.82 \\ \hline
		Pu242 & .0487 & 89.6 \\ \hline
	\end{tabular}
	\caption{Plutonium From Spent Fuel}
	\label{tab:pu}
\end{table}

To create \gls{MOX}, ~9\% Pu and ~91\% depleted uranium is used.
Thus $1,721$ tons of plutonium yields $19,122$ tons of
\gls{MOX}. \Cref{tab:pu} lists the isotope, mass fraction,
and quantity of plutonium that can be obtained from the 2050 \gls{SNF} inventory.

@@

From Varaine et al., a French
ASTRID-type \gls{SFR} of capacity $600 MWe$ needs $1.225$ tons of
plutonium a year, with an initial plutonium loading of $4.9$ tons
\cite{marsaultmarie-sophie_pre-conceptual_2012}.
Thus, it can be assumed that the ASTRID reactor takes in $49$ tons of 
\gls{MOX}, and refuels a quarter of its fuel every year. Simply,
an ASTRID reactor needs $12.25$ tons of \gls{MOX} per year.

The number of SFR-years worth of fuel that can be created with
the \gls{SNF} from 2050 is $\frac{19,122t}{12.25} = 1,560 $,
assuming infinite reprocessing and \gls{MOX} fabrication capacity.

However, assuming that \gls{MOX} can be recycled indefinitely,
spent \gls{MOX} from an ASTRID reactor
contains enough plutonium to produce a \gls{MOX} fuel with
the same mass, if mixed with depleted uranium. 
Separating plutonium from spent \gls{MOX} from
an ASTRID reactor can create \gls{MOX} 
the mass of spent \gls{MOX}, given sufficient tailings supply.

@@

\Cref{fig:pu_demand} shows the separated plutonium demand
for \gls{MOX} production to fuel the ASTRID reactors given the deployment schedule.

\begin{figure}[htbp!]
	\begin{center}
		\includegraphics[width=\columnwidth]{./images/french-transition/pu_total_demand.png}
	\end{center}
	\caption{Separated Plutonium demand for \gls{MOX} production}
	\label{fig:pu_demand}
\end{figure}

\begin{table}[h]
	\centering
	\scalebox{0.86}{
		\begin{tabular}{|c|c|c|}
			\hline
			Category [unit] & Value & Specifics \\ \hline
			Total MOX used [t] & 164,141 & \\ \hline
			Total MOX from UOX Waste [t] & 19,136.2  &   \\ \hline
			Total MOX from MOX Waste [t] & 145,004.8 & \\ \hline
			Total Tailings used [t] & 149,368.3 & \\ \hline
			Total legacy SNF reprocessed [t] & 183,992 & \\ \hline
		\end{tabular}}
		\caption {\gls{SFR} Simulation Results}
		\label{tab:sfr_sim_result}
\end {table}
